---
title: "Generalized Linear Modelings with Little Bag of Bootstraps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blbglm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
```

# Using this Library: `blbglm()`

The GLM variant works much in the same way that `blblm()` does. Below is a quick run through of each of the major features related to `blbglm()`. Similar to `glm`, the default `family = gaussian` unless otherwise specified. 

Further documentation can be found at `?blbglm`


`blbglm(formula, data, family = "gaussian", m = 10, B = 5000)`

```{r warning=FALSE}
# Create a model with m subsets, each bootstrapped B times. 
data(iris)

# Gaussian Case
blbglm(Sepal.Width~ Species, #numeric by factor 
              data = iris, m = 2, B = 100)

# Binomial Case
bi_iris <- iris[1:100,] # binomial
fit <- blbglm(formula = Species ~ Sepal.Width+Sepal.Length, 
              data = bi_iris, family ="binomial", m = 2, B = 100)

#
# Notes: Convergence errors gave this dataset some pretty wild coefficients
#         and sigmas. Per Randy, these errors are suppress, as the error 
#         handling is in place in glm1(). In short, this wasn't the best 
#         dataset to test with, but it shows the project's functionality.

```


## Print

Returning the formula can be completed with `print()`. 

`print(x, ...)`

```{r}
# Print the formula model
print(fit)

```

The standard deviation can be called with `sigma()`. Default values to return the confidence interval are false. When requested, the confidence interval can be toggled with `confidence = TRUE` with default `level = 0.95`, unless otherwise specified. 

## Sigma 

`sigma(object, confidence = FALSE, level = 0.95, ...)`

```{r}

# Return sigma without CI
sigma(fit)

# return sigma with CI
sigma(fit, confidence =TRUE)

# return sigma with 90% CI
sigma(fit, confidence =TRUE, level = .90)

```


## Coefficients 

The coefficients of the set can be called with `coef()`

`coef(object, ...)`

```{r}
coef(fit)

```

Confidence intervals for the coefficients are calculated with `confint()`. By default, the function will return a 95% confidence interval unless otherwise specified. The argument `parm` specifies which parameters should return coefficient confidence intervals.  

`confint(object, parm = NULL, level = 0.95, ...)`

```{r}
# Coefficient Confidence Interal, default alpha = 0.05
confint(fit)

# Coefficient Confidence Interal, alpha = 0.10
confint(fit, level = 0.90)

```


## Predictions

Predictions work through the command `predict()`. The new data, `newdata`, can be a single value or matrix of values. A confidence interval option can be toggled with `confidence = TRUE` with default `level=0.95`. 

`predict(object, newdata, confidence = FALSE, level = 0.95, ...)`

```{r}

# Single Value prediction
predict(fit, iris[4,])

# Take a random sampling  of ten points from the iris data
X <- iris[sample(seq_len(150), 10),]
head(X)

# Fit the values to our model
predict(fit, X)

# Fit them with a confidence interval 
predict(fit, X, confidence = TRUE)


```