---
title: "Linear Regression with Little Bag of Bootstraps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blblm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE, message = FALSE}
library(blblm)
library(tidyverse)   # for analysis 
library(knitr)       # for pretty tables

data(iris)
set.seed(1020)
```

# Using this Library: `blblm`

This library takes features similar to `lm(formula, data, ...)` with the added feature of including `m` subsamples and `B` bootstraps.

`blblm(formula, data, m = 10, B = 5000)`

```{r}
# Create a model with m subsets, each bootstrapped B times. 
fit <- blblm(Sepal.Length ~ Petal.Width + Petal.Length, data = iris, m = 10, B = 15)

# Works with interactions as well 
blblm(Sepal.Length ~ Petal.Width + Petal.Length + Petal.Width * Petal.Length, 
        data = iris, m = 10, B = 15)

```


## Print

Returning the formula can be completed with `print()`. 

`print(x, ...)`

```{r}
# Print the formula model
print(fit)

```

The standard deviation can be called with `sigma()`. Default values to return the confidence interval are false. When requested, the confidence interval can be toggled with `confidence = TRUE` with default `level = 0.95`, unless otherwise specified. 

## Sigma 

`sigma(object, confidence = FALSE, level = 0.95, ...)`

```{r}
# Return sigma without CI
sigma(fit)

# return sigma with CI
sigma(fit, confidence =TRUE)

# return sigma with 90% CI
sigma(fit, confidence =TRUE, level = .90)

```


## Coefficients 

The coefficients of the set can be called with `coef()`

`coef(object, ...)`

```{r}
coef(fit)

```

Confidence intervals for the coefficients are calculated with `confint()`. By default, the function will return a 95% confidence interval unless otherwise specified. The argument `parm` specifies which parameters should return coefficient confidence intervals.  

`confint(object, parm = NULL, level = 0.95, ...)`

```{r}

# Coefficient Confidence Interal, default alpha = 0.05
confint(fit)

# Coefficient Confidence Interal, alpha = 0.10
confint(fit, level = 0.90)

# Return only first and second coef CI's
confint(fit, parm = 1) # Just the Petal.Width
```


## Predictions

Predictions work through the command `predict()`. The new data, `newdata`, can be a single value or matrix of values. A confidence interval option can be toggled with `confidence = TRUE` with default `level=0.95`. 

`predict(object, newdata, confidence = FALSE, level = 0.95, ...)`

```{r}

# Single Value prediction
predict(fit, iris[4,])

# Take a random sampling  of ten points from the iris data
X <- iris[sample(seq_len(150), 10),]
head(X)

# Fit the values to our model
predict(fit, X)
plot(predict(fit,X), X[,1]) # Plotted values

# Fit them with a confidence interval 
predict(fit, X, confidence = TRUE)

```



## Added Features

### GLM Modeling
Similar to base R linear models, `blblm` has a `glm` extension. The glm functions are can be found under `vignette("blbglm")`. 


### Helper Functions

`est_df(object, value)`

The primary function methods `sigma(fit)` and `coef(fit)` call on helper `est_df` to create a dataframe of their respective values. The function minimizes code duplication and improves call times, particularly for functions calling for the estimate value's mean and confidence interval collectively.  

Example: `sigma_df <- est_df(fit, "sigma")`


## Sources 

sta141c-notes/ch08-bootstrap/blb.html
sta141c-notes/ch08-bootstrap/bootstrap.html