---
title: "blblm Background and Motivation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{blblm_Background_and_Motivation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE, message = FALSE}
library(blblm)
library(tidyverse)   # for analysis 
library(knitr)       # for pretty tables

data(iris)
```

## Background 

The bag of little bootstraps (BLB) is a procedure that takes the best of subsampling and bootstrapping to yield a robust and efficient analytical tool. BLB's primary use is for assessing the quality of estimators.^[sta141c-notes/ch08-bootstrap/blb.html]

### Subsampling

Subsampling works by taking random samples from the dataset on which to perform analysis.

To take a sample from a dataframe, using the iris data, the function `sample()` is performed on the rows of `iris`:

```{r sampling}
set.seed(1020)

m = 10             # Break data up into m subsample
n = nrow(iris)/m   #   with each s containing n samples 

a_sample = iris[sample(nrow(iris), n, replace = TRUE),] 
kable(
  head(a_sample)
)                               # Preview of one subsample

kable(
  nrow(a_sample),               #  with n samples
  col.names = "Subsample Size") 
```

### Bootstrapping

Bootstrapping is a tool used to increase the number of iterations or instances of a dataset. By resampling, with replacement, our original data, we can create a data set that is highly similar to our data. The additional iterations help to improve error estimates.^[sta141c-notes/ch08-bootstrap/bootstrap.html] 

In the sample below, we can compare the traditional means of collecting a confidence interval about the correlation between iris petal length and width using `cor.test()`:

```{r oldci}

# Find the dataset correlation bet petal features
cor <- round(with(iris, cor(Petal.Width, Petal.Length)),4)

# Return the confidence interval bounds for our single sample of irises
ci <-  with(iris, cor.test(Petal.Width, Petal.Length)$conf.int) 

```

The result for the confidence interval for correlation `r paste0("(", round(ci[1],4), ", ", round(ci[2],4),")")` about correlation value `r cor`.

Bootstrapping mimics how any original dataset would act. By taking the mean of `B` datasets, which originate from sampling with replacement of our original data, we can improve the precision and reduce the error that our original sample may be unintentionally bringing to the analysis. 

```{r bootstrapci, cache = TRUE}
library(rsample) # for bootstrapping 

# Create 10,000 resamples of the iris data
boots <- bootstraps(iris, times = 10)

# Calculate the error for bootstrapped CI
se <- boots %>%        # From our list of 10,000 samples
  pull(splits) %>%     #  With each sampling
  map_dbl(
    ~ {
      train_data <- analysis(.)
      with(train_data, cor(Petal.Width, Petal.Length))   # Collect the correlation
    }
  ) %>%
  sd()                                                   #  and report the error 

# Calculate the upper and lower bounds
cib <- with(iris, cor(Petal.Width, Petal.Length)) + 1.96 * c(-1, 1) * se
```

Bootstrapping narrowed the confidence band, giving us the slightly narrower interval `r paste0("(", round(cib[1],4), ", ", round(cib[2],4),")")` about the correlation of petal features, `r cor`. 

## Motivation 

While both subsampling and bootstrapping both powerful tools, combining the two can increase accuracy through the creation of similar-yet-original datasets. 

This package is designed for intuitive usage, particularly for users familiar with generalized linear modelling tools in R. 


